### 2016-08-10 thesis_paper/source.tex
Modified bunch of things regarding styling of the paper

\linespread{2}

\titleformat{\chapter}[display]
        {\normalfont\Large\bfseries\centering}{\chaptertitlename\ \thechapter}{0pt}{\Large\uppercase}

@@

%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%

\begin{document}

%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%
%   TITLEPAGE
%
%   due to variety of titlepage schemes it is probably better to make titlepage manually
%
%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%---%%%
\thispagestyle{empty}

{%%%
\sffamily
\centering

{\Large 
Parallelization of Push-based System for Molecular Simulation Data Analysis with GPU
}

\vspace{1.5cm}

{
by
}
\vspace{.5cm}

@@

\vspace{3.5cm}

@@

Department of Computer Science and Engineering

College of Engineering

@@

\vspace{3.5cm}
Major Professor:  Yicheng Tu, Ph.D.
\vspace{\fill}

\vspace{.5cm}
Date of Approval:

N/A
\vspace{\fill}

Copyright \textcopyright\space 2016, Iliiazbek Akhmedov

%%%
}%%%

\newgeometry{left=20mm,right=20mm,top=35mm,bottom=35mm}

\textbf{DEDICATION}
\vspace{0.5cm}

@@

\pagestyle{plain}
\centering
\textbf{ACKNOWLEDGMENTS}
\vspace{0.5cm}

@@

\linespread{1}

\tableofcontents

\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures

@@

\linespread{2}
\clearpage

\addcontentsline{toc}{chapter}{\abstractname} 
\begin{abstract}
\justify
\hspace{3em} Modern simulation systems generate big amount of data, which consequently has to be analyzed in a timely fashion. Traditional database management systems follow principle of pulling the needed data, processing it, and then returning the results. This approach is then optimized by means of caching, storing in different structures, or doing some sacrifices on precision of the results to make it faster. When it comes to the point of doing various queries that require analysis  of the whole data,  this design has the following disadvantages: considerable overhead on traditional disk random I/O framework while reading from the simulation output files and low throughput of the data that consequently results in long latency, and, if there was any indexing to optimize selections, overhead of storing those becomes too big, too. Besides it, indexing will also cause delay during write operations and since most of the queries work with the entire data sets, indexing loses its point.

@@

@@

It is noticable that growth of the speedup is not stable and with certain number of atoms it drops dramatically. It is because we've used static approach of computing grid dimensions. Besides it, in the future, it can be expanded into a dynamic version that will automatically adjust the grid dimensions choosing least overhead that it has to go with.

>>>>

\titleformat{\chapter}[display]{\normalfont\Large\bfseries\centering}{\chaptertitlename\ \thechapter}{0pt}{\Large\uppercase}

@@

\begin{document}
{
\thispagestyle{empty}

\linespread{1}\selectfont
\centering
\vspace*{5\baselineskip}
Parallelization of Push-based System for

\vspace*{1\baselineskip}

Molecular Simulation Data Analysis with GPU 
\vspace*{3\baselineskip}

%{ by }
\vspace*{3\baselineskip}

@@

\vspace*{5\baselineskip}

@@

Department of Computer Science and Engineering College of Engineering

@@

\vspace*{3\baselineskip}
Major Professor:  Yicheng Tu, Ph.D.

\vspace*{2\baselineskip}
\vspace{.5cm}
Date of Approval:

N/A

\vspace*{3\baselineskip}
Keywords: data processing, cuda optimization, big data,

streaming

\vspace*{1\baselineskip}
Copyright \textcopyright\space 2016, Iliiazbek Akhmedov

}

\clearpage
\pagestyle{plain}
\centering

\vspace*{5\baselineskip}
\linespread{2}\selectfont
\textbf{DEDICATION}

\vspace*{1\baselineskip}

@@

\linespread{1}\selectfont
\vspace*{5\baselineskip}

\textbf{ACKNOWLEDGMENTS}

\vspace*{1\baselineskip}

\linespread{2}\selectfont

@@

\linespread{1}\selectfont
\tableofcontents

\linespread{2}\selectfont
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures

@@

\linespread{1}\selectfont
\vspace*{5\baselineskip}

\addcontentsline{toc}{chapter}{\abstractname}

\vspace*{1\baselineskip}

\linespread{2}\selectfont

\begin{abstract}
\justify
\hspace{3em} Modern simulation systems generate big amount of data, which consequently has to be analyzed in a timely fashion. Traditional database management systems follow principle of pulling the needed data, processing it, and then returning the results. This approach is then optimized by means of caching, storing in different structures, or doing some sacrifices on precision of the results to make it faster. When it comes to the point of doing various queries that require analysis  of the whole data,  this design has the following disadvantages: considerable overhead on traditional disk random I/O framework while reading from the simulation output files and low throughput of the data that consequently results in long latency, and, if there was any indexing to optimize selections, overhead of storing those becomes too big, too. Besides it, indexing will also cause delay during write operations and since most of the queries work with the entire data sets, indexing loses its point.

@@

\subsection{SDH resolution performance impact}

@@

It is noticable that growth of the speedup is not stable and with certain number of atoms it drops dramatically. One of possible reasons could the fact that we've used static approach of computing grid dimensions. Besides it, in the future, it can be expanded into a dynamic version that will automatically adjust the grid dimensions choosing least overhead that it has to go with.
